FTLR proof cases

### 2018-03-09 fully-abstract-comp/ftlr-proof-cases.tex
First step for load case.
Preparatory work on load case for FTLR

@@

\paragraph{Case: $\protect\tload{\trg{r_1}}{\trg{r_2}}$}

>>>>

\begin{definition}[purePart]
  For any world $W$, we define
  \begin{align*}
    \purePart{W} &\defeq (\purePart{\pwheap},\purePart{\pwpriv},\purePart{\pwfree})\\
    \purePart{W_\var{heap}} &\defeq
                       \begin{cases}
                         W_{\var{heap}}(r) & \text{if } W_\var{heap}(r) = (pure,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_\var{heap}(r) = (\spatial,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_\var{heap}(r) = (\spatialo,\var{sm})\\
                         \revoked & \text{if } W_\var{heap}(r) = \revoked\\
                       \end{cases}\\
    \purePart{W_\var{priv}} &\defeq
                       \begin{cases}
                         ((\spatial,\var{sm}),\sigma) & \text{if } W_\var{priv}(r) = ((\spatial,\var{sm}),\sigma)\\
                         ((\spatial,\var{sm}),\sigma) & \text{if } W_\var{priv}(r) = ((\spatialo,\var{sm}),\sigma)\\
                         (\revoked,\sigma) & \text{if } W_\var{priv}(r) = (\revoked,\sigma)\\
                       \end{cases}
    \purePart{W_\var{free}} &\defeq
                       \begin{cases}
                         W_{\var{free}}(r) & \text{if } W_{\var{free}}(r) = (pure,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_{\var{free}}(r) = (\spatial,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_{\var{free}}(r) = (\spatialo,\var{sm})\\
                         \revoked & \text{if } W_{\var{free}}(r) = \revoked\\
                       \end{cases}
  \end{align*}

\end{definition}
\begin{lemma}[purePart is pure]
 For all $W$, we have that $W = W \oplus \purePart{W}$.
\end{lemma}

\begin{lemma}[non-linear words are pure]
  If $\npair{(w_1,w_2)} \in \lrv{W}$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv{\purePart{W}}$.
\end{lemma}

\begin{lemma}[load from capability works]
  \label{lem:readcond-writecond-work}
  If
  \begin{itemize}
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$
  \item $c = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $\npair{(c,c)}\in\lrv(H_\sigma,W)$
  \item $W \oplus W_M$ is defined
  \item $n' < n$
  \item $w_S = \linCons{\ms_S(a)}$, $w_T = \linCons{\ms_T(a)}$
  \item $\linConsPerm{\perm}$
  \end{itemize}
  Then $\exists W', W_M'\ldotp$
  Additionally, if
  \begin{itemize}
  \item $W_M = W' \oplus W_M'$
  \item $\memSat{(\ms_S\update{\mem.a}{w_S},\stk,\ms_\stk,\ms_T\update{\mem.a}{w_T})}{W_M'}$
  \item $\npair{(\ms_S(a),\ms_T(a))} \in \lrv(W')$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

\paragraph{Case: $\protect\tload{\trg{r_1}}{\trg{r_2}}$}
Since $\Phi_S\not\step\failed$, we have that $\Phi_S \step \Phi_S' \term[i-1]$ and one of the following cases hold: 
\begin{itemize}
\item \[\Phi_S' = \updPcAddr{\Phi\update{\mem.a}{w_2}\updReg{r_1}{w}}\]
  with $\Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$ 
  $\perm \in \readAllowed{}$, $\withinBounds{\Phi(r_2)}$, $w = \Phi.\mem(a)$ and $w_2 = \linCons{w}$ and $\linConsPerm{w,\perm}$
\item \[\Phi_S' = \updPcAddr{\Phi \update{\ms_\stk.a}{w_2}\updReg{r_1}{w}}\]
  with $\Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, $\perm \in \readAllowed{}$, $\withinBounds{\Phi(r_2)}$, $\aaddr \in \dom(\Phi.\ms_\stk)$, $w = \Phi.\ms_\stk(a)$ and $w_2 = \linCons{w}$ and $\linConsPerm{w,\perm}$
\end{itemize}
